\documentclass[a4paper,10pt]{article}

%--------------- includes ---------------------
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage[big]{layaureo}		% better formatting of the A4 page
\usepackage{titlesec}			% custom \section
\usepackage{hyperref}			% internal href
\usepackage{tabularx}
\usepackage[bottom]{footmisc}

\usepackage[absolute]{textpos}
\usepackage[usenames]{xcolor}

%---------------- finetuning -----------------
\pagestyle{empty}				% non-numbered pages

% CV Sections inspired by:
% http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{5pt}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

\definecolor{linkcolour}{rgb}{0.26, 0.5, 0.72}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%------------------------ CV -------------------------
\begin{document}
{\centering{\Huge Aleksandr Ilin}\par}


%------------------- PERSONAL INFORMATION -------------------
\section{Personal Information}
\begin{tabularx}{\textwidth}{lX}
	Date of Birth:	& December 23, 1992 \\
	Address:		& Saint-Petersburg, Russia \\
	Email:			& \href{mailto:alexander.ilin.92@gmail.com} {alexander.ilin.92@gmail.com} \\
	Telegram:		& \href{https://t.me/sasha_ilin} {@sasha\_ilin} \\
\end{tabularx}


%------------------- TECHNICAL SKILLS -------------------
\section{Technical Skills}
\begin{tabular}{ll}
	Programming Languages:	& Python3, C++, \{z,ba\}sh \\
	Python Frameworks:		& Django, DRF, Flask, SQLAlchemy, scipy, pandas, sklearn \\
	OS:						& Linux \\
	VCS:					& Git, SVN \\
	Other:					& Git-Flow, Docker, Design Patterns, UML, Scrum, Kanban
\end{tabular}


%------------------- WORK EXPERIENCE -------------------
\section{Work Experience}
\textcolor{gray}{Total: 3 year 2 months} \\
\begin{tabularx}{\textwidth}{lX}
	Jun 2016 -				&	Programmer \\
	Present					&	\textbf{Luxoft}, Saint-Petersburg,
								\href{www.luxoft.com}{www.luxoft.com} \\
	\textcolor{gray}
	{2 year}	
							&	\footnotesize{
									Leading a small project team (3 developers, 1 QA).\newline
									Managing a project for the test automation framework development.\newline
									Communication with the customer, scrum planning.\newline
									Building a complicated distributed system: researches, implementation.\newline\newline

									Redesigned existing solution:\newline
									* reworked the system architecture;\newline
									* optimized test algorithms;\newline
									* integrated best deploying practices;\newline
									* migrated from SVN to Git;\newline
									* set up the development infrastructure and VCS usage best practises.\newline\newline
									Stack: Python3.5, Django, DRF, Celery, RabbitMQ/Redis, PostgreSQL, bash, Ubuntu16+, Docker, Git, SVN.\newline
								} \\

	\multicolumn{2}{c}{}\\

	Dec 2015 -				&	Scientific Programmer \\
	May 2016				&	\textbf{Navmii}, Saint-Petersburg,
								\href{www.navmii.com}{www.navmii.com} \\
	\textcolor{gray}
	{6 months}
							&	\footnotesize{
									Researches of the neural network models and ML algorithms for the classification of road signs and cars, based on the real-time visual content.\newline
									* Developing ML algorithms.\newline
									* Analysing ML algorithms working results.\newline
									* Reporting researches and results points.\newline
									* Proposing the new approaches to try.\newline
									* Improving and optimising algorithms and data sets.\newline\newline
									ETL, feature selection, feature engineering, developing and implementation of ML
									algorithms.\newline
									Developed several utilities on python for data preprocessing (adding noise,
									statistics collection, visualization, etc).\newline
								} \\

	\multicolumn{2}{c}{}\\	

	Aug - Dec 2015			&	Python Developer\\
	\textcolor{gray}
	{5 months}		
							&	\textbf{Тензор, ООО}, Yaroslavl,
								\href{www.tensor.ru}{www.tensor.ru} \\
							&	\footnotesize{
									Taked a participation in buidling a complicated distributed system for the interaction of business processes, documents and business participants through a one communication network.\newline\newline
									Taked a participation in designing and development of a subsystem of user
									notifications via various channels (e.g. sms, email, push).\newline
									* implemented and refactored backend (C++, PostgreSQL, Python)\newline
									* optimized database structure;\newline
									* support of messages transformation algorithms (xslt);\newline
									* frontend logic support (JS);\newline
									* provided system support.\newline
								} \\
	
	\multicolumn{2}{c}{}\\

	Jan - Mar 2013			&	Erlang Intern \\
	\textcolor{gray}
	{3 months}
							&	\textbf{LiveTex}, Saint-Petersburg,
								\href{www.livetex.ru}{www.livetex.ru} \\
							& 	\footnotesize{
									Implemented unit tests for the SIP protocol messaging module. Detection and covering non-trivial cases.
								} \\
\end{tabularx}


%------------------- LANGUAGES -------------------
\section{Languages}
\begin{tabular}{ll|l}
	Russian:				& \multicolumn{2}{l}{Mothertongue} \\
	English\footnotemark :	& Listening				& C1 \\
							& Reading				& C1 \\
							& Spoken interaction	& B1 \\
							& Spoken production		& B1 \\
							& Writing				& B1 \\
	
\end{tabular}
\footnotetext{Self-assessment. Common European Framework of Reference(CEF) level}


%------------------- EDUCATION -------------------
\section{Education}
\begin{tabularx}{\textwidth}{lX}
	June, 2018:		& Master, \textbf{ITMO University}, Saint-Petersburg \\
					& Major:  High Performance Computing \\

	\multicolumn{2}{c}{}\\

	June, 2015:		& Specialists, \textbf{ITMO University}, Saint-Petersburg \\
					& Major:  Information Systems and Technologies
\end{tabularx}


%------------------- PERSONAL DETAILS -------------------
\section{Personal Details}
\begin{tabularx}{\textwidth}{l} % :<
Purposeful, hardworking, curious. I prefer to work taking care of my code and keeping it clean.\\
A python developer, also familiar and working with: с++, bash, lua, js, sql.\\
I like the following principles: Unix way, The Zen of Python, ABC, KISS.\\
An advanced user of linux-systems. (not having deep knowledge, but can gladly solve a problem \\if having enough time).\\
Having an experience in ML/DL/CV/Agent Modeling.\\
\\
Github profile: \href{https://github.com/cjcjcj}{github.com/cjcjcj} 
\end{tabularx}

\end{document}
